systemfit: A Package to Estimate\\ Simultaneous Equation Systems in \proglang{R}

### 2006-02-14 paper/trunk/systemfit_intro.tex
really small change after read. it's ready for submission!
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@589 591db2bd-e0a0-4d22-8c19-2192dbb7da31

Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions. These restrictions can be
tested and/or imposed only in a simultaneous estimation approach
especially the economic theory suggests many cross-equation
restrictions. (But we don't say why this is important...) Are we
imposing restrictions in the parameters, or the variance-covariance
matrix or both and for what pupose?

For all of the methods developed in the package, the disturbnaces of
the individual equations are assumed to be independent and identially
distributed (iid).  
In the future, we would like to add the ability to fit equations were
the disturbances are serially correlated (wikins 1969).

@@

This paper is organized as follows: In section~\ref{sec:Estimation} we
introduce the mathematics of estimating equation systems.
Section~\ref{sec:Restrictions} shows how linear restrictions can be
imposed.
Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit}, especially how the features presented in the previous
sections can be used.
All other relevant issues are discussed in section~\ref{sec:Other}.
Finally, a summary and outlook are presented in
section~\ref{sec:Summmary}.

>>>>

Another reason to estimate an equation system simultaneously are
cross-equation parameter restrictions. These restrictions can be
tested and/or imposed only in a simultaneous estimation approach
especially the economic theory suggests many cross-equation
restrictions.

% (But we don't say why this is important...) Are we
% imposing restrictions in the parameters, or the variance-covariance
% matrix or both and for what pupose?

% For all of the methods developed in the package, the disturbnaces of
% the individual equations are assumed to be independent and identially
% distributed (iid).  
% In the future, we would like to add the ability to fit equations were
% the disturbances are serially correlated (wikins 1969).

@@

This paper is organized as follows: In Section~\ref{sec:Estimation} we
introduce the mathematics of estimating equation systems.
Section~\ref{sec:Restrictions} shows how linear restrictions can be
imposed.  Section~\ref{sec:Usage} demonstrates how to run
\pkg{systemfit}, especially how the features presented in the previous
sections can be used.  All other relevant issues are discussed in
Section~\ref{sec:Other}.  Finally, a summary and outlook are presented
in Section~\ref{sec:Summmary}.

### 2006-02-14 paper/trunk/systemfit_other.tex
made seemingly massive changes... but hopefully not for the worse...
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@586 591db2bd-e0a0-4d22-8c19-2192dbb7da31
really small change after read. it's ready for submission!
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@589 591db2bd-e0a0-4d22-8c19-2192dbb7da31

@@

@@

Hausman \citep{hausman78} developed a test have power against
alternatives for which $\hat{\theta}$ and $\tilde{\theta}$ diverge
under misspecification.
The resulting test statistic, distributed as a
$\chi^2$, is the difference between the covariance of an
efficient and the covariance of the inefficient estimator is zero, if the
model is correctly specified.

The test is based on the idea that under the hypothesis of no
correlation, both the limited information estimates and the
full-information results are consistent, but only the full-information
estimates are efficient and under the alternative, the limited
information estimates are consistent, but the full information
estimates are not.

@@

\begin{equation}
m = ( b_2 - b_3 )^{'} ( V_2 - V_3 ) ( b_2 - b_3 ) 
\label{eq:hausman}
\end{equation}
where $b_2$ and $V_2$ are the estimated coefficients and the
variance-covariance matrix from a 2SLS estimation and $b_3$ and $V_3$
are the estimated coefficients and their variance covariance-matrix
from a 3SLS estimation.

@@

As linear systems of equations can be estimated using
\code{systemfit}, nonlinear systems of equations \citep{hausman75}
can be estimated using a similar function \code{nlsystemfit}.
The usage for the nonlinear estimation function is similar to
\code{systemfit} and can estimate system of equations using OLS, SUR,
2SLS and 3SLS methods.

@@

where \code{method} is one of the following estimation methods: "OLS",
"SUR", "2SLS", or "3SLS", \code{eqns} is a list of equations similar
to those described for \code{systemfit}, and \code{start} is a list of
starting values of the parameter estimates.
The nlsystemfit function relies on \code{nlm} to perform the minimization
of the objective functions and the \code{qr} set of functions.
If the user does not have a set of estimates for the initial parameters,
it is suggested using linearized forms in one of the linear methods,
or simply using \code{nls} to obtain estimates for the equations.

>>>>

Don't we already mention this in the usage section.

@@

\paragraph{Degrees of freedom for t-tests}   
\code{probdfsys} use the degrees of freedom of the whole system
   (in place of the degrees of freedom of the single equation)
   to calculate prob values for the t-test of individual parameters.

@@

Hausman \citep{hausman78} developed a test have power against
alternatives for which $\hat{\theta}$ and $\tilde{\theta}$ diverge
under misspecification.  The resulting test statistic, distributed as
a $\chi^2$, is the difference between the covariance of an efficient
estimator and the covariance of the inefficient estimator. If the
difference is zero, the model is correctly specified.

The test is based on the idea that under the null hypothesis of no
correlation, both the limited information estimates and the
full-information results are consistent, but only the full-information
estimates are efficient and under the alternative, the limited
information estimates are consistent, but the full information
estimates are not.

@@

\begin{equation}
m = ( \beta_2 - \beta_3 )^{'} ( \Omega_2 - \Omega_3 ) ( \beta_2 - \beta_3 ) 
\label{eq:hausman}
\end{equation}
where $\beta_2$ and $\Omega_2$ are the estimated coefficients and the
variance-covariance matrix from a 2SLS estimation and $\beta_3$ and
$\Omega_3$ are the estimated coefficients and their variance
covariance-matrix from a 3SLS estimation.

@@

As linear systems of equations can be estimated using
\code{systemfit}, nonlinear systems of equations \citep{hausman75} can
be estimated using a similar function; \code{nlsystemfit}.  The usage
for the nonlinear estimation function is similar to \code{systemfit}
and can estimate system of equations using OLS, SUR, 2SLS and 3SLS
methods. The equations are defined as,

@@

where \code{method} is one of the following estimation methods: "OLS",
"SUR", "2SLS", or "3SLS", \code{eqns} is a list of equations similar
to those described for \code{systemfit}, and \code{start} is a list of
starting values of the parameter estimates.  The nlsystemfit function
relies on \code{nlm} to perform the minimization of the objective
functions and the \code{qr} set of functions.  If the user does not
have a set of estimates for the initial parameters, it is suggested
using linearized forms in one of the linear methods, or simply using
\code{nls} to obtain estimates for the equations. The outputs are
similar to those obtained by \code{systemfit} objects.
